Analysis

### 2022-05-25 EDA_SCREEN.Rmd
Adjust SCREEN data processing

# Input files
# Human CTCF-bound cCRE (hg38)
fileNameIn1 <- file.path(dir_data, "data/GRCh38-CTCF.bed")
# download.file("https://api.wenglab.org/screen_v13/fdownloads/cCREs/GRCh38-CTCF.bed", fileNameIn1)
# Mouse CTCF-bound cCRE (mm10)
fileNameIn2 <- file.path(dir_data, "data/mm10-CTCF.bed")
# download.file("https://api.wenglab.org/screen_v13/fdownloads/cCREs/mm10-CTCF.bed", fileNameIn2)
# Output files
fileNameOut1 <- file.path(dir_data, "results/CTCF_hg38_SCREEN.RData")
fileNameOut2 <- file.path(dir_data, "results/CTCF_mm10_SCREEN.RData")
```

@@

# Save as RData object. subdir is the character name of the CTCF GRanges variable
save(list = mtx_to_gr(mtx = mtx_human, genome_id = "hg38"), file = fileNameOut1)
save(list = mtx_to_gr(mtx = mtx_mouse, genome_id = "mm10"), file = fileNameOut2)
# load(file = paste0(subdir, ".RData"))
```

>>>>

# Input files
# Human CTCF-bound cCRE (hg38)
fileNameIn1 <- file.path(dir_data, "data/GRCh38-CTCF.bed")
# download.file("https://api.wenglab.org/screen_v13/fdownloads/cCREs/GRCh38-CTCF.bed", fileNameIn1)
# Mouse CTCF-bound cCRE (mm10)
fileNameIn2 <- file.path(dir_data, "data/mm10-CTCF.bed")
# download.file("https://api.wenglab.org/screen_v13/fdownloads/cCREs/mm10-CTCF.bed", fileNameIn2)
# Output files
fileNameOut1 <- file.path(dir_data, "results/hg38.SCREEN.GRCh38_CTCF.RData")
fileNameOut2 <- file.path(dir_data, "results/mm10.SCREEN.mm10_CTCF.RData")
```

@@

hg38.SCREEN.GRCh38_CTCF <- mtx_to_gr(mtx = mtx_human, genome_id = "hg38")
length(hg38.SCREEN.GRCh38_CTCF)
summary(width(hg38.SCREEN.GRCh38_CTCF))
mm10.SCREEN.mm10_CTCF <- mtx_to_gr(mtx = mtx_mouse, genome_id = "mm10")
length(mm10.SCREEN.mm10_CTCF)
summary(width(mm10.SCREEN.mm10_CTCF))

# Save as RData object. subdir is the character name of the CTCF GRanges variable
save(list = hg38.SCREEN.GRCh38_CTCF, file = fileNameOut1)
save(list = mm10.SCREEN.mm10_CTCF, file = fileNameOut2)
# load(file = paste0(subdir, ".RData"))
```
